Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-21 article_review/Manuscript.tex
minor changes

\newcommand{\comment}[1]{{\color{cyan} #1 }}
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

When dealing with complex numerical models, analytical expressions of Sobol' indices are often inaccessible. In such cases, one must rely on an estimation of these indices. The original estimation procedure is due to Sobol' \cite{Sobol'}. However, this procedure requires several model evaluations which are usually expensive. Later on, Saltelli \cite{Saltelli} proposed strat\-egies to estimate sets of Sobol' indices at once through the use of a combinatorial formalisms. While elegant, these strat\-egies still require a large number of model evaluations.  A cost efficient alternative to estimate first-order indices was introduced in \cite{Mara}. This alternative, called the replication procedure, has recently been further studied  in \cite{Tissot} and generalized to the estimation of closed second-order indices.

@@

%The problem of interest is the evaluation of first-order and total effect Sobol' indices.
In our framework, we are only interested in single input indices, namely $|u|=1$. The computation of the normalized indices is performed based on the following integral formulas for their numerators:
{\color{purple}
\begin{align}
\label{first.order}
\underline{\tau}_u^2  &= \int_{[0,1]^{2d}} \left(
f(\vx_u:{\vx'}_{-u})-f(\vx')\right)f(\vx)d\vx d{\vx'}, \\
\label{total.effect}
\ov{$\tau$}_u^2 &= \frac{1}{2}\int_{[0,1]^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2 d\vx_u d{\vx'}, \ u \in \mathcal{D},
\end{align}
}
while variance and mean of $f$ are evaluated as:
\begin{gather}
\begin{aligned}
\sigma^2 &= \int_{[0,1]^{d}} f(\vx)^2d{\vx} - \mu^2, \\
 \mu &= \int_{[0,1]^{d}} f(\vx) d{\vx},
\label{eq.sigma.mu}
\end{aligned}
\end{gather}
Usually the complexity of $f$ causes the solution of integrals \eqref{first.order}, (\ref{total.effect}) and (\ref{eq.sigma.mu}) to be intractable. In such cases, one can instead estimate these quantities.

\subsection{Estimation of Sobol' indices}
\label{sec:2.2}
In this section we review two Monte Carlo procedures for the estimation of Sobol' indices. A design is a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ where each point is obtained by sampling each variable $x_j$ $n$ times. Each row of the design is a point $\vx_i$ in $[0,1]^d$ and each column of the design refers to samples of a variable $x_j$. Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid \mathcal{U}([0,1]^{2d})$. One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
{\color{purple}
\begin{align}
\label{first.order.est}
\widehat{\underline{\tau}_u^2} &= \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_{i,u}:{\vx'}_{i,-u})-f(\vx'_i)\right)f(\vx_i),\\
\label{total.effect.est}
\widehat{\ov{$\tau$}_u^2} &= \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
\end{align}
}
using for $\sigma^2$:
{\color{purple} 
\begin{equation}
 \widehat{\sigma}^2 = \frac{1}{n-1} \sum \limits_{i=0}^{n-1} \left( f(\vx_i) - \widehat{\mu}\right)^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i).
\label{mu.est}
\end{equation}
}
Then, the Sobol' indices estimators are:
\begin{equation}
\widehat{\underline{S}}_u = \widehat{\underline{\tau}_u^2} / \widehat{\sigma}^2, \qquad
\widehat{\overline{S}}_u = \widehat{\overline{\tau}_u^2} / \widehat{\sigma}^2.
\label{common.sobol.est}
\end{equation}
Using this method, the estimation of a single pair ($\widehat{\underline{S}}_u$, $\widehat{\overline{S}}_u$) requires $3n$ evaluations of the model $f$. Thus, for all first order and total effect indices, one would need $3nd$ model evaluations. Using a combinatorial formalism, in \cite{Saltelli} Saltelli proposes the following estimation strategy:
\begin{theorem}
\label{saltelli.theorem}
The $d+2$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allow to estimate all first-order and total effect Sobol' indices at a cost of $n(d+2)$ evaluations of the model.
\end{theorem}
The main idea of the theorem is that there is no need to reevaluate $f({\vx}_i)$ and $f({\vx'}_i)$ for each $u$. Hence, we can simply evaluate $f({\vx}_i)$ $n$ times, $f({\vx'}_i)$ $n$ times, and $f(\vx_{i,u}:{\vx'}_{i,-u})$ $nd$ times, which accounts for the $n(d+2)$ evaluations.

The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ {\color{purple}according} to $u$. While elegant, this approach requires a number of model evaluations that grows linearly with respect to the input space dimension.

@@

\subsection{Extension to Sobol' indices}
\label{sec:3.2}
In this section we will extend the definition of the error bound (\ref{errbd}) to Sobol' indices. To achieve this goal, we consider the two integral formulas of the first-order and total effect Sobol' indices with $|u|=1$:
%\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
%In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
{\color{purple}
\begin{align*}
\underline{S}_u(\vI) & = \frac{\int_{[0,1]^{2d}} \left(f(\vx_u:{\vx'}_{-u})-f(\vx')\right)f(\vx)d\vx d{\vx'}}{\int_{[0,1]^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1]^{d}} f(\vx) d{\vx}\right)^2}, \\ 
\underline{S}_u(\vI) & = \frac{I_1}{I_3-(I_4)^2}, \\
\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1]^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx_u d{\vx'}}{\int_{[0,1]^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1]^{d}} f(\vx) d{\vx}\right)^2}, \\
\overline{S}_u(\vI) & = \frac{I_2}{I_3-(I_4)^2},
\end{align*}
}
where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values. Indices $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$. If we estimate $\vI$ by $\widehat{\vI}$ with known error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$, $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.

Then, as an alternative to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
\begin{gather}
\begin{aligned}
\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\underline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_undersu}
\end{gather}
and,
\begin{gather}
\begin{aligned}
\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\overline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_oversu}
\end{gather}
Because numerator and denominator are both known to be positive, maximizing $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp. $I_2$) and minimizing the denominator $I_3-I_4^2$. Analogously, to minimize $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) one minimizes the numerator $I_1$ (resp. $I_2$) and maximizes the denominator $I_3-I_4^2$. As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_2(\vI)$ given the true value of $I_1$ for the test function of Bratley \textit{et al.} \cite{Bratley}. This function is further described in Section \ref{sec:5}. 
\begin{figure}[t]
\caption{The delimited region in the figure represents the possible values of $\underline{S}_2$ for $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ (Bratley \textit{et al.} function). There, $\underline{S}_2^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),0\Big{)}$, $\underline{S}_2^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),1\Big{)}$, and $\widehat{\underline{S}}_2=(\underline{S}_2^{\min}+\underline{S}_2^{\max})/2$.}
\centering
\includegraphics[width=.5\textwidth]{estimator_3d_small.eps}
\label{fig:1}       % Give a unique label
\end{figure}

@@

\comment{For this article, we assumed that evaluating the model is expensive. Hence, to study the cost we will focus on the number of function evaluations needed to estimate the indices. The function values used to estimate the indices are also used to compute the discrete Walsh coefficients. Thus, there are no additional evaluations required to compute the error bound. The only computation cost that could be expensive is the fast Walsh transform. However, on a regular laptop, if we consider an extreme case of obtaining $2^{20}$ model values ($\approx$ one million points):
\begin{itemize}
\item At an average evaluation time of $1$ microsecond per point, the total evaluation time is about $1$ second.
\item The fast transform applied to these values takes around $0.5$ seconds.
\end{itemize}
In practice, we focus on models that will take much more than $1$ microsecond to evaluate and hence, the fast transform cost becomes inexpensive.
}

@@

The cost of our algorithm, in terms of model evaluations, varies whether Variant $A$ or Variant $B$ is selected. To discuss this cost we note by $m^\star$ the ending iteration. If Variant $A$ is selected, the cost of our algorithm is:
\[\sum \limits_{u \in \mathcal{D}} 2^{m_u} + 2 \times 2^{m^{\star}}, \qquad m^\star= \max \limits_{u \in \mathcal{D}} \ m_u,\]
where: 
\begin{itemize}
\item[$\bullet$] $2^{m_u}$ is the number of evaluations $f\left(\vx_{i,u}:{\vx'}_{i,-u}\right)$ used to estimate both the first-order index $\underline{S}_u$ and the total effect index $\overline{S}_u$,
\item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect indices.
\end{itemize}
If all $m_u$ are equal, the cost of Variant $A$ becomes $2^{m^\star}(d+2)$ and we recover the cost specified in Theorem \ref{saltelli.theorem} with $n=2^{m^\star}$.

If Variant $B$ is selected, the cost of our algorithm equals $2 \times 2^{m^{\star}}$. This cost corresponds to the one of the replication procedure introduced in Section \ref{sec:2.2}, where $2n=2\times 2^{m^{\star}}$ independent of $d$.

@@

When $\underline{S}_u$ is small, it usually becomes harder to estimate. For this reason, we consider the use of a new estimator to evaluate small first-order Sobol' indices in Variant $A$. This estimator called ``Correlation 2" has been introduced by Owen in \cite{Owen}. In this article, he discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices. Our aim is to show that the use of ``Correlation 2" in Variant $A$ {\color{purple}  improves the estimation of small first-order indices while potentially reducing the total number of model evaluations required.} This new estimator is,
\begin{equation*}
\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i)).
\end{equation*}
\comment{As proposed by Owen in \cite{Owen}, the sample points are $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$. For our algorithm, we extend Owen's estimator by replacing the uniform points with a scrambled Sobol' sequence in dimension $3d$. In either case, this estimator requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.}
\bigskip

@@

The two classical test functions considered in this article are {\color{purple} a non qMC (quasi-Monte Carlo) friendly version of the} g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}. The idea is to test our method over two categories of functions: additive (Bratley \textit{et al.} function) and multiplicative (g-function).

@@

{\color{purple} Table \ref{comparison.bratley} shows the average number of evaluations performed in Variant $A.a$ to estimate $\underline{S}_u$ and $\ov{$S$}_u$. The column $N$ indicates the number of times where $\ov{$S$}_u$ required more evaluations than $\underline{S}_u$. In this case, we observe that $\ov{$S$}_u$ requires more evaluations than $\underline{S}_u$ in only $4$ of the $600$ estimations.
\begin{table}[t]
\caption{Average number of evaluations performed to estimate $\underline{S}_u$ and $\ov{$S$}_u$ in Variant $A.a$. Column $N$ shows the number of times among the $100$ repeats where $\ov{$S$}_u$ required more evaluations than $\underline{S}_u$.}
\centering
\begin{tabular}{cccc}
\hline
 input & $\underline{S}_u$ & $\ov{$S$}_u$ & $N$ \\ \hline
 $x_1$ & $16876$ & $16384$ & $0$ \\  \hline
 $x_2$ & $8520$ & $8192$ & $0$ \\  \hline
 $x_3$ & $4096$ & $2786$ & $0$ \\  \hline
 $x_4$ & $3794$ & $1096$ & $4$ \\  \hline
 $x_5$ & $635$ & $512$ & $0$ \\  \hline
 $x_6$ & $712$ & $512$ & $0$ \\ 
\hline 
\end{tabular}
\label{comparison.bratley}
\end{table}
\begin{table}[t]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$, failure rates $r_{\delta_{\underline{S}_u}}$, and averaged total number of evaluations for Variant $B$.}
\centering
\begin{tabular}{cccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ \\ \hline
 $x_1$ & $0.6529$ &  $0.0004$ & $0$ \\ \hline
 $x_2$ & $0.1791$ &  $0.0006$ & $0$ \\ \hline
 $x_3$ & $0.0370$ &  $0.0007$ & $0$ \\ \hline
 $x_4$ & $0.0133$ &  $0.0037$ & $0.25$    \\ \hline
 $x_5$ & $0.0015$ & $0.0023$ & $0$  \\ \hline
 $x_6$ & $0.0015$ & $0.0025$ & $0$  \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $65 \ 536$}\\ \hline 
\end{tabular}
\label{res.bratley.B}
\end{table}}

>>>>

\newcommand{\comment}[1]{{\color{purple} #1 }}
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

When dealing with complex numerical models, analytical expressions of Sobol' indices are often inaccessible. In such cases, one must rely on an estimation of these indices. The original estimation procedure is due to Sobol' \cite{Sobol'}. \break However, this procedure requires several model evaluations which are usually expensive. Later on, Saltelli \cite{Saltelli} proposed strat\-egies to estimate sets of Sobol' indices at once through the use of a combinatorial formalisms. While elegant, these strat\-egies still require a large number of model evaluations.  A cost efficient alternative to estimate first-order indices was introduced in \cite{Mara}. This alternative, called the replication procedure, has recently been further studied  in \cite{Tissot} and generalized to the estimation of closed second-order indices.

@@

%The problem of interest is the evaluation of first-order and total effect Sobol' indices.
In our framework, we are only interested in single input indices, namely $|u|=1$. The computation of the normalized indices is performed based on the following integral formulas for their numerators:
\begin{align}
\label{first.order}
\underline{\tau}_u^2  &= \int_{[0,1]^{2d}} \left(
f(\vx_u:{\vx'}_{-u})-f(\vx')\right)f(\vx)d\vx d{\vx'}, \\
\label{total.effect}
\ov{$\tau$}_u^2 &= \frac{1}{2}\int_{[0,1]^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2 d\vx_u d{\vx'}, \ u \in \mathcal{D},
\end{align}
while variance and mean of $f$ are evaluated as:
\begin{gather}
\begin{aligned}
\sigma^2 &= \int_{[0,1]^{d}} f(\vx)^2d{\vx} - \mu^2, \\
 \mu &= \int_{[0,1]^{d}} f(\vx) d{\vx},
\label{eq.sigma.mu}
\end{aligned}
\end{gather}
Usually the complexity of $f$ causes the solution of integrals \eqref{first.order}, (\ref{total.effect}) and (\ref{eq.sigma.mu}) to be intractable. In such cases, one can instead estimate these quantities.

\subsection{Estimation of Sobol' indices}
\label{sec:2.2}
In this section we review two Monte Carlo procedures for the estimation of Sobol' indices. A design is a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ where each point is obtained by sampling each variable $x_j$ $n$ times. Each row of the design is a point $\vx_i$ in $[0,1]^d$ and each column of the design refers to samples of a variable $x_j$. Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid \mathcal{U}([0,1]^{2d})$. One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
\begin{align}
\label{first.order.est}
\widehat{\underline{\tau}_u^2} &= \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_{i,u}:{\vx'}_{i,-u})-f(\vx'_i)\right)f(\vx_i),\\
\label{total.effect.est}
\widehat{\ov{$\tau$}_u^2} &= \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
\end{align}
using for $\sigma^2$:
{\color{purple} 
\begin{equation}
 \widehat{\sigma}^2 = \frac{1}{n-1} \sum \limits_{i=0}^{n-1} \left( f(\vx_i) - \widehat{\mu}\right)^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i).
\label{mu.est}
\end{equation}
}
Then, the Sobol' indices estimators are:
\begin{equation}
\widehat{\underline{S}}_u = \widehat{\underline{\tau}_u^2} / \widehat{\sigma}^2, \qquad
\widehat{\overline{S}}_u = \widehat{\overline{\tau}_u^2} / \widehat{\sigma}^2.
\label{common.sobol.est}
\end{equation}
Using this method, the estimation of a single pair ($\widehat{\underline{S}}_u$, $\widehat{\overline{S}}_u$) requires $3n$ evaluations of the model $f$. Thus, for all first order and total effect indices, one would need $3nd$ model evaluations. Using a combinatorial formalism, in \cite{Saltelli} Saltelli proposes the following estimation strategy:
\begin{theorem}
\label{saltelli.theorem}
The $d+2$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allow to estimate all first-order and total effect Sobol' indices at a cost of $n(d+2)$ evaluations of the model.
\end{theorem}
The main idea of the theorem is that there is no need to reevaluate $f({\vx}_i)$ and $f({\vx'}_i)$ for each $u$. Hence, we can simply evaluate $f({\vx}_i)$ $n$ times, $f({\vx'}_i)$ $n$ times, and $f(\vx_{i,u}:{\vx'}_{i,-u})$ $nd$ times, which accounts for the $n(d+2)$ evaluations.

The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ {\color{purple}according} to $u$. While elegant, this approach requires a number of model evaluations that grows linearly with respect to the input \break space dimension.

@@

\subsection{Extension to Sobol' indices}
\label{sec:3.2}
In this section we will extend the definition of the error bound (\ref{errbd}) to Sobol' indices. To achieve this goal, we consider the two integral formulas of the first-order and total effect Sobol' indices with $|u|=1$:
%\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
%In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
\begin{align*}
\underline{S}_u(\vI) & = \frac{\int_{[0,1]^{2d}} \left(f(\vx_u:{\vx'}_{-u})-f(\vx')\right)f(\vx)d\vx d{\vx'}}{\int_{[0,1]^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1]^{d}} f(\vx) d{\vx}\right)^2}, \\ 
\underline{S}_u(\vI) & = \frac{I_1}{I_3-(I_4)^2}, \\
\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1]^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx_u d{\vx'}}{\int_{[0,1]^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1]^{d}} f(\vx) d{\vx}\right)^2}, \\
\overline{S}_u(\vI) & = \frac{I_2}{I_3-(I_4)^2},
\end{align*}
where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values. Indices $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$. If we estimate $\vI$ by $\widehat{\vI}$ with known error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$, $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.

Then, as an alternative to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
\begin{gather}
\begin{aligned}
\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\underline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_undersu}
\end{gather}
and,
\begin{gather}
\begin{aligned}
\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\overline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_oversu}
\end{gather}
Because numerator and denominator are both known to be positive, maximizing $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) is done through \break maximizing the numerator $I_1$ (resp. $I_2$) and minimizing the denominator $I_3-I_4^2$. Analogously, to minimize $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) one minimizes the numerator $I_1$ (resp. $I_2$) and maximizes the denominator $I_3-I_4^2$. As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_2(\vI)$ given the true value of $I_1$ for the test function of Bratley \textit{et al.} \cite{Bratley}. This function is further described in Section \ref{sec:5}. 
\begin{figure}[t]
\caption{The delimited region in the figure represents the possible values of $\underline{S}_2$ for $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ (Bratley \textit{et al.} function). There, $\underline{S}_2^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),0\Big{)}$, $\underline{S}_2^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),1\Big{)}$, and $\widehat{\underline{S}}_2=(\underline{S}_2^{\min}+\underline{S}_2^{\max})/2$.}
\centering
\includegraphics[width=.45\textwidth]{estimator_3d_small.eps}
\label{fig:1}       % Give a unique label
\end{figure}

@@

\comment{It is important to note that the function evaluations performed to estimate the Sobol' indices are also used to compute the discrete Walsh coefficients. As a result, no additional function evaluations is required to compute the error bound. The only computation cost that could be expensive is the fast Walsh transform. However, the fast transform cost becomes inexpensive when dealing with models that will take much more than $1$ microsecond to evaluate.}
%For this article, we assumed that evaluating the model is expensive. Hence, to study the cost we will focus on the number of function evaluations needed to estimate the indices. The function values used to estimate the indices are also used to compute the discrete Walsh coefficients. Thus, there are no additional evaluations required to compute the error bound. The only computation cost that could be expensive is the fast Walsh transform. However, on a regular laptop, if we consider an extreme case of obtaining $2^{20}$ model values ($\approx$ one million points):
%\begin{itemize}
%\item At an average evaluation time of $1$ microsecond per point, the total evaluation time is about $1$ second.
%\item The fast transform applied to these values takes around $0.5$ seconds.
%\end{itemize}
%In practice, we focus on models that will take much more than $1$ microsecond to evaluate and hence, the fast transform cost becomes inexpensive.
%}

@@

The cost of our algorithm, in terms of model evaluations, varies whether Variant $A$ or Variant $B$ is selected. To discuss this cost we note by $m^\star$ the ending iteration. If Variant $A$ is selected, the cost of our algorithm is:
\[\sum \limits_{u \in \mathcal{D}} 2^{m_u} + 2 \times 2^{m^{\star}}, \qquad m^\star= \max \limits_{u \in \mathcal{D}} \ m_u,\]
where: 
\begin{itemize}
\item[$\bullet$] $2^{m_u}$ is the number of evaluations $f\left(\vx_{i,u}:{\vx'}_{i,-u}\right)$ used to estimate both the first-order index $\underline{S}_u$ and the total effect index $\overline{S}_u$,
\item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect indices.
\end{itemize}
If all $m_u$ are equal, the cost of Variant $A$ becomes $2^{m^\star}(d+2)$ and we recover the cost specified in Theorem \ref{saltelli.theorem} with $n=2^{m^\star}$.
If Variant $B$ is selected, the cost of our algorithm equals $2 \times 2^{m^{\star}}$. This cost corresponds to the one of the replication procedure introduced in Section \ref{sec:2.2}, where $2n=2\times 2^{m^{\star}}$ independent of $d$.

@@

When $\underline{S}_u$ is small, it usually becomes harder to estimate. For this reason, we consider the use of a new estimator to evaluate small first-order Sobol' indices in Variant $A$. This estimator called ``Correlation 2" has been introduced by Owen in \cite{Owen}. In this article, he discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices. Our aim is to show that the use of ``Correlation 2" in Variant $A$ {\color{purple}  improves the estimation of small first-order indices while potentially reducing the total number of model evaluations required.} This new estimator is,
\begin{equation*}
\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i)).
\end{equation*}
\comment{As proposed by Owen in \cite{Owen}, the sample points are \break $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$. For our algorithm, we extend \break Owen's estimator by replacing the uniform points with a scrambled Sobol' sequence in dimension $3d$. In either case, this estimator requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.}
\bigskip

@@

The two classical test functions considered in this article are {\color{purple} a non qMC (quasi-Monte Carlo) friendly version of the} g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}. The idea is to test our method over two categories of functions: additive (Bratley \textit{et al.}) and multiplicative (g-function).

@@

{\color{purple} Table \ref{comparison.bratley} shows the average number of evaluations performed in Variant $A.a$ to estimate $\underline{S}_u$ and $\ov{$S$}_u$. The column $N$ indicates the number of times where $\ov{$S$}_u$ required more evaluations than $\underline{S}_u$. In this case, we observe that $\ov{$S$}_u$ requires more evaluations than $\underline{S}_u$ in only $4$ of the $100$ estimations.
\begin{table}[t]
\caption{Average number of evaluations performed to estimate $\underline{S}_u$ and $\overline{S}_u$ in Variant $A.a$. Column $N$ shows the number of times among the $100$ repeats where $\overline{S}_u$ required more evaluations than $\underline{S}_u$.}
\centering
\begin{tabular}{cccc}
\hline
 input & $\underline{S}_u$ & $\overline{S}_u$ & $N$ \\ \hline
 $x_1$ & $16876$ & $16384$ & $0$ \\  \hline
 $x_2$ & $8520$ & $8192$ & $0$ \\  \hline
 $x_3$ & $4096$ & $2786$ & $0$ \\  \hline
 $x_4$ & $3794$ & $1096$ & $4$ \\  \hline
 $x_5$ & $635$ & $512$ & $0$ \\  \hline
 $x_6$ & $712$ & $512$ & $0$ \\ 
\hline 
\end{tabular}
\label{comparison.bratley}
\end{table}
\begin{table}[t]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$, failure rates $r_{\delta_{\underline{S}_u}}$, and averaged total number of evaluations for Variant $B$.}
\centering
\begin{tabular}{cccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ \\ \hline
 $x_1$ & $0.6529$ &  $0.0004$ & $0$ \\ \hline
 $x_2$ & $0.1791$ &  $0.0006$ & $0$ \\ \hline
 $x_3$ & $0.0370$ &  $0.0007$ & $0$ \\ \hline
 $x_4$ & $0.0133$ &  $0.0037$ & $0.25$    \\ \hline
 $x_5$ & $0.0015$ & $0.0023$ & $0$  \\ \hline
 $x_6$ & $0.0015$ & $0.0025$ & $0$  \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $65 \ 536$}\\ \hline 
\end{tabular}
\label{res.bratley.B}
\end{table}}
